MSE Scenarios for short and long lived

### 2025-04-16 Scenarios.Rmd
Cheng's corrections

@@

# Set initial NAA for each stock
log_N1  <- rep(10, n_stocks) # Create difference between stocks
N1_pars <- generate_ini_N1(log_N1,basic_info,ini.opt)

# Set mean recruitment para. for each stock
mean_rec_par <- list()
for (i in 1:n_stocks) mean_rec_par[[i]] <- exp(log_N1[i])

@@

mods[[2]] = loop_through_fn(om = om_with_data,
                            em_info = info, 
                            random = random,
                            M_em = M, # use OM M
                            sel_em = sel, # use OM sel
                            NAA_re_em = NAA_re_em, # use rec assumed random around the mean instead, help runtime (est B-H is difficult)
                            move_em = NULL,
                            age_comp_em = "multinomial",
                            # Here is the correct code: separate.em = FALSE also works for one-area model
                            em.opt = list(separate.em = FALSE, separate.em.type = 1, 
                                          do.move = FALSE, est.move = FALSE),
                            assess_years = assess.years, 
                            assess_interval = assess.interval, 
                            base_years = base.years,
                            year.use = 30, # number of years of data you want to use in the assessment model
                            add.years = TRUE, # extends assessment time series instead of moving window of year.use years
                            seed = 123,
                            save.sdrep = FALSE, 
                            save.last.em = TRUE,
                            FXSPR_init = 0.01) # IMPORTANT!

@@

par(mfrow = c(1,2))
SSB_s1 <- lapply(mods, function(mod) mod$om$rep$SSB[,1])
plot(SSB_s1[[1]], type = "l", col = "blue", ylab = "SSB", xlab = "Year", ylim=c(0,100000), main = "OM SSB") 
colors <- c("red","green","purple","orange")
for (i in length(SSB_s1)) {
  lines(SSB_s1[[i]], col = colors[i-1],lty = i)
}
legend("topleft",legend = paste0("EM ", 1:2), col = c("blue",colors),lty=1:5, cex=0.8)

Catch_s1 <- lapply(mods, function(mod) mod$om$rep$pred_catch[,1])
plot(Catch_s1[[1]], type = "l", col = "blue", ylab = "Catch", xlab = "Year", ylim=c(0,30000), main = "OM Catch")
colors <- c("red","green","purple","orange")
for (i in length(Catch_s1)) {
  lines(Catch_s1[[i]], col = colors[i-1],lty = i)
}

>>>>

# --------------------------------------------------- #
# ------- Do we need to change fracyr_spawn? -------- #
#    Fraction of the year when spawning is now 0.625  #
# --------------------------------------------------- #

@@

# Set initial NAA for each stock
log_N1  <- rep(10, n_stocks) # Create difference between stocks

# ------------------------------------------------------ #
# ------------- Below code has been changed ------------ #
# ------------------------------------------------------ #

N1_pars <- generate_ini_N1(basic_info = basic_info, ini.opt = "equilibrium", log_N1 = log_N1, log_N1_F = 0.1)
# WE MAY NEED TO HAVE A MORE SENSIBLE INITIAL NUMBERS AT AGE (now is using default: Number of age 1 = exp(10))

# ------------------------------------------------------ #
# ------------- Above code has been changed ------------ #
# ------------------------------------------------------ #

# Set mean recruitment para. for each stock
mean_rec_par <- list()
for (i in 1:n_stocks) mean_rec_par[[i]] <- exp(log_N1[i]) #

# ------------------------------------------------------ #
# ------ WE MAY NEED A SENSIBLE MEAN RECREUITMENT ------ #
# ------------------------------------------------------ #

@@

mods[[2]] = loop_through_fn(om = om_with_data,
                            em_info = info, 
                            random = random,
                            M_em = M, # use OM M
                            sel_em = sel, # use OM sel
                            NAA_re_em = NAA_re_em, # use rec assumed random around the mean instead, help runtime (est B-H is difficult)
                            move_em = NULL,
                            age_comp_em = "multinomial",
                            # Here is the correct code: separate.em = FALSE also works for one-area model
                            em.opt = list(separate.em = FALSE, separate.em.type = 1, 
                                          do.move = FALSE, est.move = FALSE),
                            # ------------------------------------------------------ #
                            # - Below is needed when making changes on data quality- #
                            # ------------------------------------------------------ #
                            update_index_info  = list(agg_index_sigma = agg_index_sigma, index_Neff = index_Neff), # Must have this!
                            update_catch_info  = list(agg_catch_sigma = agg_catch_sigma, catch_Neff = catch_Neff), # Must have this!
                            # ------------------------------------------------------ #
                            # - Above is needed when making changes on data quality- #
                            # ------------------------------------------------------ #
                            assess_years = assess.years, 
                            assess_interval = assess.interval, 
                            base_years = base.years,
                            year.use = 30, # number of years of data you want to use in the assessment model
                            add.years = TRUE, # extends assessment time series instead of moving window of year.use years
                            seed = 123,
                            save.sdrep = FALSE, 
                            save.last.em = TRUE,
                            FXSPR_init = 0.01) # IMPORTANT!

@@

par(mfrow = c(1,2))
SSB_s1 <- lapply(mods, function(mod) mod$om$rep$SSB[,1])
plot(SSB_s1[[1]], type = "l", col = "blue", ylab = "SSB", xlab = "Year", ylim=c(0,100000), main = "OM SSB", lwd = 2) 
colors <- c("red","green","purple","orange")
lines(SSB_s1[[2]], col = colors[2],lty = 2, lwd = 2)
legend("topleft",legend = paste0("EM ", 1:2), col = c("red","green"),lty=1:2, cex=0.8)

Catch_s1 <- lapply(mods, function(mod) mod$om$rep$pred_catch[,1])
plot(Catch_s1[[1]], type = "l", col = "blue", ylab = "Catch", xlab = "Year", ylim=c(0,15000), main = "OM Catch", lwd = 2)
colors <- c("red","green","purple","orange")
lines(Catch_s1[[2]], col = colors[2],lty = 2, lwd = 2)
